---
title: "codewindow Example"
format:
  revealjs: 
    footer: <https://github.com/emilhvitfeldt/quarto-revealjs-codewindow>
revealjs-plugins:
  - codewindow
echo: true
code-line-numbers: false
knitr: true
---

## Basic usage

Everything starts with wrapping a codeblock with `.codewindow` fenced div. So

````` markdown
::: {.codewindow}
```{{scss}}
.pink {
  color: pink;
}
```
:::
`````

becomes

::: {.codewindow}

```{scss}
.pink {
  color: pink;
}
```
:::

## file name on file tab

THe file name can be specified by writing the name as plain text inside the `codewindow` div. So

````` markdown
::: {.codewindow}
styles.scss
```{{scss}}
.pink {
  color: pink;
}
```
:::
`````

becomes

::: {.codewindow}
styles.scss
```{scss}
.pink {
  color: pink;
}
```
:::

## File icon

Adding a css class to the `.codewindow` div will add icon if supported. so 

````` markdown
::: {.codewindow .sass}
styles.scss
```{{scss}}
.pink {
  color: pink;
}
```
:::
`````

becomes

::: {.codewindow .sass}
styles.scss
```{scss}
.pink {
  color: pink;
}
```
:::

## File icons

::: columns
::: {.column width="50%"}

::: {.codewindow .r}
script.R
```{sass}
```
:::

::: {.codewindow .rmd}
report.Rmd
```{sass}
```
:::

::: {.codewindow .python}
script.py
```{sass}
```
:::

::: {.codewindow .js}
script.js
```{sass}
```
:::

::: {.codewindow .julia}
script.jl
```{sass}
```
:::

:::

::: {.column width="50%"}

::: {.codewindow .quarto}
index.qmd
```{sass}
```
:::

::: {.codewindow .html}
index.html
```{sass}
```
:::

::: {.codewindow .css}
styles.css
```{sass}
```
:::

::: {.codewindow .sass}
styles.sass
```{sass}
```
:::

:::
:::

## File icons

::: columns
::: {.column width="50%"}

::: {.codewindow .terminal}
script.sh
```{sass}
```
:::

::: {.codewindow .nextflow}
main.nf
```{sass}
```
:::

:::

::: {.column width="50%"}

::: {.codewindow .stan}
model.stan
```{sass}
```
:::

::: {.codewindow .mplus}
model.inp
```{sass}
```
:::

:::
:::

## File icons

::: columns
::: {.column width="50%"}

::: {.codewindow .sql}
query.sql
```{sass}
```
:::

::: {.codewindow .markdown}
README.md
```{sass}
```
:::

::: {.codewindow .yaml}
_quarto.yml
```{sass}
```
:::

:::

::: {.column width="50%"}

::: {.codewindow .json}
data.json
```{sass}
```
:::

::: {.codewindow .git}
.gitignore
```{sass}
```
:::

::: {.codewindow .bash}
deploy.bash
```{sass}
```
:::

:::
:::

## File icons

::: columns
::: {.column width="50%"}

::: {.codewindow .sas}
analysis.sas
```{sass}
```
:::

::: {.codewindow .spss}
survey.sps
```{sass}
```
:::

::: {.codewindow .stata}
regress.do
```{sass}
```
:::

:::

::: {.column width="50%"}

::: {.codewindow .matlab}
solve.m
```{sass}
```
:::

::: {.codewindow .cpp}
kernel.cpp
```{sass}
```
:::

::: {.codewindow .fortran}
solver.f90
```{sass}
```
:::

:::
:::

## File icons

::: columns
::: {.column width="50%"}

::: {.codewindow .typescript}
app.ts
```{sass}
```
:::

::: {.codewindow .rust}
main.rs
```{sass}
```
:::

:::

::: {.column width="50%"}

::: {.codewindow .go}
server.go
```{sass}
```
:::

:::
:::

## Setting width

The `width` argument is natively supported, so the width can be set like so:

````` markdown
::: {.codewindow .sass width="350px"}
styles.scss
```{{scss}}
.pink {
  color: pink;
}
```
:::
`````

becomes

::: {.codewindow .sass width="350px"}
styles.scss
```{scss}
.pink {
  color: pink;
}
```
:::

## Setting colors

The colors of a single window can be set with the `bg`, `header-bg`, `tab-bg`, `tab-active-bg`, `color` and `shadow-color` arguments:

````` markdown
::: {.codewindow .sass bg="#fdf6e3" header-bg="#eee8d5" shadow-color="#93a1a1"}
styles.scss
```{{scss}}
.pink {
  color: pink;
}
```
:::
`````

becomes

::: {.codewindow .sass bg="#fdf6e3" header-bg="#eee8d5" shadow-color="#93a1a1"}
styles.scss
```{scss}
.pink {
  color: pink;
}
```
:::

## Dark windows

The `.codewindow-dark` class is a preset for dark decks:

::: {.codewindow .sass .codewindow-dark}
styles.scss
```{scss}
.pink {
  color: pink;
}
```
:::

To restyle every window in the deck, set the same custom properties in your own stylesheet:

````` css
.reveal {
  --codewindow-bg: #1e293b;
  --codewindow-header-bg: #0f172a;
  --codewindow-tab-bg: #334155;
  --codewindow-color: #e2e8f0;
}
`````

## Multiple blocks in one window

A codewindow can hold more than one code block (and text between them); nothing gets dropped. So

````` markdown
::: {.codewindow .r}
my-script.R
```{{r}}
runif(1)
```

Then some more code:

```{{r}}
runif(42)
```
:::
`````

## Multiple blocks in one window

becomes

::: {.codewindow .r}
my-script.R
```{r}
runif(1)
```

Then some more code:

```{r}
runif(42)
```
:::

## Multiple tabs

Wrap several `.editor` divs in a `.codewindow` to get one file tab per editor. Add `.active` to pick which starts open (the first otherwise), and `.fragment` to focus the next tab as the slide advances.

````` markdown
:::: {.codewindow}
::: {.editor .r name="Final (updated) - USE THIS ONE - .R"}
```r
data <- read.csv("my-data.csv")
```
:::

::: {.editor .r .fragment name="01-clean.R"}
```r
library(dplyr)
data <- filter(data, x > 0)
```
:::
::::
`````

## Only the best names

:::: {.codewindow}
::: {.editor .r name="00-load.R"}

```r
data <- read.csv("my-data.csv")
```
:::

::: {.editor .r .fragment name="01-clean.R"}
```r
library(dplyr)
data <- filter(data, x > 0)
```
:::
::::

## Multiple tabs

becomes (advance the slide to switch tabs)

:::: {.codewindow}
::: {.editor .r name="00-load.R"}
```r
data <- read.csv("my-data.csv")
```
:::

::: {.editor .r .fragment name="01-clean.R"}
```r
library(dplyr)
data <- filter(data, x > 0)
```
:::

::: {.editor .r .fragment name="02-plot.R"}
```r
library(ggplot2)
ggplot(data, aes(x, y)) +
  geom_point()
```
:::
::::

## Additional notes

These divs should work like any other divs. So you can pass in other styles with `styles=""` and use [absolute position](https://quarto.org/docs/presentations/revealjs/advanced.html#absolute-position)

See next slide for examples

## Additional notes

::: {.codewindow .sass .absolute top="70%" left="35%" width="350px"}
styles.scss
```{scss}
.pink {
  color: pink;
}
```
:::

::: {.codewindow .sass .absolute top="35%" left="10%" width="350px" style="transform: rotate(-15deg);"}
styles.scss
```{scss}
.yellow {
  color: yellow;
}
```
:::

::: {.codewindow .sass .absolute top="35%" left="60%" width="350px" style="transform: rotate(15deg);"}
styles.scss
```{scss}
.blue {
  color: blue;
}
```
:::
